\Title

### 2021-01-22 manuscript/manuscript.tex
Make a single figure data and grid for Australia
Joining them makes it easier to compare the observations with the
interpolation results. Also added bathymetry as a background and tweaked
the font and frame sizes.

% Define style for urls
\urlstyle{same}

@@

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground
(see Fig.~\ref{fig:australia-data-gravity}).

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-gravity.png}
    \caption{
        Gravity data for Australia composed by more than 1.7 million
        observations on ground \citep{wynne2018}. The data is available under
        the Creative Commons Attribution 4.0 International Licence.
    }
    \label{fig:australia-data-gravity}
\end{figure*}

First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (see Fig.~\ref{fig:australia-data-disturbance}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
as reference.
Then we obtain plain coordinates of the observation points by applying
a Mercator projection.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-data-disturbance.png}
    \caption{
        Gravity disturbance of Australia computed as the difference between
        observed gravity and normal gravity generated by the WGS84 ellipsoid on
        each observation point.
    }
    \label{fig:australia-data-disturbance}
\end{figure*}

@@

Finally, the equivalent sources are used to predict the values of the gravity
disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid
(see Fig.~\ref{fig:australia-grid}).

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia-grid.png}
    \caption{
        Interpolated gravity disturbance of Australia on a regular grid at
        \AustraliaEqlGridHeight{} over the ellipsoid. The interpolated values
        were obtained through gradient-boosted equivalent sources.
    }
    \label{fig:australia-grid}
\end{figure*}

\section{Software implementation}

We have implemented the methods described in the previous sections though
a software written in Python language.
The code for generating the results of this work are available in
\url{https://doi.org/10.6084/m9.figshare.13604360}.
The gradient-boosted equivalent sources implementation is based on the
non-boosted sources available through the Harmonica library
\citep{harmonica2020}, part of the Fatiando a Terra project
\citep{fatiando2013}.
Another Python libraries were used:
Verde \citep{verde2018} to apply block reductions and managing coordinates,
Boule \citep{boule2020} for computing normal gravity,
Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
multidimensional datasets and numerical
computations,
Numba \citep{numba2015} for writing pre-comipled implementations and
parallelization,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures.

>>>>

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia.png}
    \caption{
      Pseudo-color maps of observed (left) and
      interpolated (right) gravity disturbance of Australia.
      Observations are part of a compilation by \citet{wynne2018} of
      over 1.7 million ground gravity measurements.
      Interpolated values were obtained through gradient-boosted equivalent
      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
      over the WGS84 ellipsoid.
    }
    \label{fig:australia}
\end{figure*}

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground.
First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (Fig.~\ref{fig:australia}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
as reference.
Then we obtain planar coordinates of the observation points by applying
a Mercator projection.

@@

Finally, the equivalent sources are used to predict the values of the gravity
disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid
(Fig.~\ref{fig:australia}).
